|

### 2023-05-31 manuscript/Chapter2-appendix1.Rmd
update appendix 1

output: 
  word_document:
    reference_docx: Chapter2-styles-appendix.docx
    fig_caption: yes
bibliography: references2.bib
csl: ecology.csl
---

@@

b_draws[, c(31:33) := NULL]

@@

# plogis for the success parameters
b_draws[
  , c("b_successnovice_Intercept",
      "b_successinterm_Intercept",
      "b_successadvanced_Intercept",
      "b_successnovice_Zgame_duration",
      "b_successinterm_Zgame_duration",
      "b_successadvanced_Zgame_duration"
  )
  := lapply(.SD, function(x) {plogis(x)}),
  .SDcols = c(
    "b_successnovice_Intercept",
    "b_successinterm_Intercept",
    "b_successadvanced_Intercept",
    "b_successnovice_Zgame_duration",
    "b_successinterm_Zgame_duration",
    "b_successadvanced_Zgame_duration"
  )
]

@@

# Create trait column
fixef_tab[
  , trait := rep(c(
    "predator speed", "predator speed",
    "prey speed", "prey speed", "hunting success"),
    6
  )
]

# Rename parameter column
fixef_tab[
  , parameter := rep(
    c(
      rep(c("intercept (mean)", "intercept (sigma)"), 2),
      "intercept (mean)",
      rep(c("prey rank (mean)", "prey rank (sigma)"), 2),
      "match duration (mean)"
    ),
    3
  )
]

@@

# Reorder columns and rows
fixef_tab <- fixef_tab[, c(1, 2, 5, 4, 3)]
table <- fixef_tab[c(3, 5, 4, 6, 7, 9, 8, 10, 1, 2)]

# Because I can't align hunting success properly
table[10, 1] <- " "

@@

  # Align repeated rows on column 1
  merge_v(j = 1) %>%
  valign(j = 1, valign = "top", part = "body") %>%

@@

  # Table caption
  set_caption(
    caption = "Table S1. Posterior medians and 95% credible intervals of the fixed effects estimated by the MDHGLM of predator speed, prey speed, and predator hunting success.",
    style = "Table Caption"
  ) %>%

>>>>

output: 
  word_document:
    reference_docx: Chapter2-styles-appendix.docx
    fig_caption: yes
bibliography: references.bib
csl: ecology.csl
---

@@

b_draws[, c(34:36) := NULL]

@@

# plogis for the success parameters
b_draws[
  , c("b_successnovice_Intercept",
      "b_successinterm_Intercept",
      "b_successadvanced_Intercept",
      "b_successnovice_Zgame_duration",
      "b_successinterm_Zgame_duration",
      "b_successadvanced_Zgame_duration",
      "b_successnovice_Zprey_avg_rank",
      "b_successinterm_Zprey_avg_rank",
      "b_successadvanced_Zprey_avg_rank"
  )
  := lapply(.SD, function(x) {plogis(x)}),
  .SDcols = c(
    "b_successnovice_Intercept",
    "b_successinterm_Intercept",
    "b_successadvanced_Intercept",
    "b_successnovice_Zgame_duration",
    "b_successinterm_Zgame_duration",
    "b_successadvanced_Zgame_duration",
    "b_successnovice_Zprey_avg_rank",
    "b_successinterm_Zprey_avg_rank",
    "b_successadvanced_Zprey_avg_rank"
  )
]

@@

# Create trait column
fixef_tab[, trait := ""][
  parameter %like% "success", trait := "hunting success"][
    parameter %like% "speed", trait := "predator speed"][
      parameter %like% "preyspeed", trait := "prey speed"
      ]

# Rename parameter column
fixef_tab[
  , parameter := rep(
    c(
      rep(c("intercept (mean)", "intercept (sigma)"), 2),
      "intercept (mean)",
      rep(c("prey rank (mean)", "prey rank (sigma)"), 2),
      "match duration (mean)", "prey rank (mean)"
    ),
    3
  )
]

@@

# Reorder columns and rows
fixef_tab <- fixef_tab[, c(1, 2, 5, 4, 3)]
table <- fixef_tab[c(4, 6, 5, 7, 8, 10, 9, 11, 1, 2, 3)]

# Because I can't align the rows properly
# in the flextable object
table[c(2:4, 6:8, 10, 11), 1] <- " "

@@

  # Align repeated rows on column 1
  #merge_v(j = 1) %>%
  valign(j = 1, valign = "top", part = "body") %>%

@@

  # Table caption
  set_caption(
    caption = "Table S1. Posterior medians and 95% HDP intervals of the fixed effects estimated by the MDHGLM of predator speed, prey speed, and predator hunting success.",
    style = "Table Caption"
  ) %>%
